---
title: "post-scan rating analyses"
author: "baf44"
date: "1/23/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

Code to plot and analyze liking and fullness ratings

This code uses the following derivative files:

(1) 
(2) 

# Setup

```{r imports, include=FALSE}
library(lme4)
library(lmerTest) # need this to get p-values with anova()
library(plyr)
library(maditr)
library(ggplot2)
library(rstatix)
library(dplyr)
library(psych)
library(emmeans)
library(stringr)
library(ggsignif)

# Source gen_likefull.R to generate byblock_full_long and byblock_like_long dataframes -- these contain liking and anticipated fullness ratings averaged by food-cue block (long format)
source("R/gen_likefull.R")

```

####  Prepare for parametric analyses #### 

The follow chunk is used to determine what subjects to exclude from parametric analyses

Subjects will be excluded if:
(1) they are missing ratings (fullness, liking) for any block
(2) they do not have enough variability in rating to be included in analyses (must have >1 unique value)

```{r identify subs to exclude}

#### Identify subs with missing ratings for any block ####

# make list subjects with missing fullness data for any block
pm_missing_fullness <- unique(byblock_full_long[is.na(byblock_full_long$avg_fullness),"id"])
pm_missing_fullness # 5 109

# make list subjects with missing behavior for any block
pm_missing_liking <- unique(byblock_like_long[is.na(byblock_like_long$avg_liking),"id"])
pm_missing_liking # 5 109

# count number of subjects with missing data
nrow(pm_missing_fullness) # N = 2
nrow(pm_missing_liking) # N = 2

#### clean data base ####

# remove subjects with missing data
pm_full_temp <- byblock_full_long[ ! byblock_full_long$id %in% pm_missing_fullness, ]
pm_like_temp <- byblock_like_long[ ! byblock_like_long$id %in% pm_missing_liking, ]

# remove runs excluded for motion
censor_sum_subset <- censor_sum[,c("id", "run", "p_censor_interest")]

pm_full_clean <- merge(x=pm_full_temp,y=censor_sum_subset, 
             by=c("id","run"))
pm_full_clean <-pm_full_clean[!(pm_full_clean$p_censor_interest>20),]

pm_like_clean <- merge(x=pm_like_temp,y=censor_sum_subset, 
             by=c("id","run"))
pm_like_clean <-pm_like_clean[!(pm_like_clean$p_censor_interest>20),]

#### Identify subs with  no variability ####

# count number of distinct fullness values by id and ED condition (high, low)
distinct_full_byED <- pm_full_clean %>% group_by(id, category) %>% dplyr::summarize(distinct = n_distinct(avg_fullness))

# count number of distinct fullness values by id and portion condition (large, small)
distinct_full_byPS <- pm_full_clean %>% group_by(id, portion) %>% dplyr::summarize(distinct = n_distinct(avg_fullness))

# count number of distinct liking values by id and ED condition (high, low)
distinct_like_byED <- pm_like_clean %>% filter(cuetype != "office") %>% 
                      group_by(id, category) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# count number of distinct liking values by id and food PS condition (large, small)
distinct_like_byPS <- pm_like_clean %>% filter(cuetype != "office") %>% 
                      group_by(id, portion) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# count number of distinct liking values by id and cue type (large, small)
distinct_like_byCue <- pm_like_clean %>% group_by(id, cuetype) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# Count subs with no variability in fullness (distinct==1) in at least 1 condition when assessing by ED
novar_full_byED <- distinct_full_byED[(distinct_full_byED$distinct==1),] %>%
  dplyr::summarize(distinct = n_distinct(id))
nrow(novar_full_byED) # N = 0

# Count subs with no variability in fullness (distinct==1) in at least 1 condition when assessing by PS
novar_full_byPS <- distinct_full_byPS[(distinct_full_byPS$distinct==1),] %>%
  dplyr::summarize(distinct = n_distinct(id))
nrow(novar_full_byPS) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by ED
novar_like_byED <- distinct_like_byED[(distinct_like_byED$distinct==1),]
nrow(novar_like_byED) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by PS
novar_like_byPS <- distinct_like_byPS[(distinct_like_byPS$distinct==1),]
nrow(novar_like_byED) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by cue type
novar_like_byCue <- distinct_like_byCue[(distinct_like_byCue$distinct==1),]
nrow(novar_like_byCue) # N = 1
novar_like_byCue$id # 73 ## ID 73 rated 0 for all office supplies


```

```{r count subs included in parametric analyses analyses}

#### count subs included in parametric analyses analyses ####
n_distinct(distinct_full_byED$id)
n_distinct(distinct_full_byPS$id)
n_distinct(distinct_like_byED$id)
n_distinct(distinct_like_byPS$id)
n_distinct(distinct_like_byCue[!(distinct_like_byCue$id==73),]$id) # remove  73 -- no variation in rating for office supplies

```


#### Behavioral analyses ####

The following code analyses liking and fullness by cue type/ED and amount and generates corresponding plots.
Ratings are assessed for all subjects included in non-parametric analyses (n=61).

# should run be numeric or categorical?

``` {r liking analyses}

# create food-only dataframe by removing office conditions
byblock_like_long_food<-byblock_like_long[!(byblock_like_long$cuetype=="office"),]

# remove NAs -- not needed to run analyses, but helpful for predicting values to plot results
byblock_like_clean<-byblock_like_long[!is.na(byblock_like_long$avg_liking),]
byblock_like_food_clean <- byblock_like_long_food[!is.na(byblock_like_long_food$avg_liking),]


#### ANALYSES ####

# should run be numeric or categorical?

# liking ~ portion*cue type (food, office)
liking_mixed_cuetype = lmer(avg_liking ~ portion*category + as.numeric(run) + (1 | id), data = byblock_like_clean)
anova(liking_mixed_cuetype)

# liking ~ portion*ED
liking_mixed_ED = lmer(avg_liking ~ portion*category + as.numeric(run) + (1 | id), data = byblock_like_food_clean)
anova(liking_mixed_ED)

# get means and ses
emmeans(liking_mixed_cuetype, specs = pairwise ~category|portion, type = "response")
emmeans(liking_mixed_ED, specs = pairwise ~category|portion, type = "response")

```

fullness analyses
``` {r fullness analyses}
# remove NAs -- not needed to run analyses, but helpful for predicting values to plot results
byblock_full_clean<-byblock_full_long[!is.na(byblock_full_long$avg_fullness),]

# fullness ~ portion size (large, small) x ED (high, low)
fullness_mixed_ED = lmer(avg_fullness ~ portion*category + as.numeric(run) + (1 | id), data = byblock_full_clean)
anova(fullness_mixed_ED)

emmeans(fullness_mixed_ED, specs = pairwise ~category|portion, type = "response")


```

Figure 1:
``` {r liking and fullness plots}

# get adjusted response after adjusting for covariates in model 
byblock_like_clean$predict_liking_mixed_cuetype <- predict(liking_mixed_cuetype, type="response")
byblock_like_food_clean$predict_liking_mixed_ED <- predict(liking_mixed_ED, type="response")
byblock_full_clean$predict_fullness_mixed_ED <- predict(fullness_mixed_ED, type="response")


quartiles_by_group <- byblock_like_clean %>%
  group_by(cuetype, portion) %>%
  summarize(
    Q1 = quantile(predict_liking_mixed_cuetype, 0.25),
    Q3 = quantile(predict_liking_mixed_cuetype, 0.75)
  )
print(quartiles_by_group)

#### VIOLIN PLOTS with ggplot####

# liking ~ amount x cue type
plot_liking_cuetype <- ggplot(byblock_like_clean, aes(x=cuetype, y=predict_liking_mixed_cuetype, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE) +
  geom_signif(comparisons = list(c("food","Office")), y_position = 110, map_signif_level = TRUE) +
  geom_boxplot(aes(group = interaction(cuetype, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Cue Type",
       y = "Adjusted liking") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(0, 125) + 
  scale_x_discrete(labels = c("food" = "Food",
                              "Office" = "Office Supplies"))

plot_liking_cuetype

# liking ~ amount x ED (category)
plot_liking_ED <- ggplot(byblock_like_food_clean, aes(x=category, y=predict_liking_mixed_ED, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE)+
  geom_signif(comparisons = list(c("HighED","LowED")), y_position = 110,
              map_signif_level = TRUE) +
  geom_boxplot(aes(group = interaction(category, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Energy Density",
       y = "Adjusted liking") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(0, 125) +
  scale_x_discrete(labels = c("HighED" = "Higher",
                              "LowED" = "Lower"))

plot_liking_ED

# fullness ~ amount x ED
plot_fullness_ED <- ggplot(byblock_full_clean, aes(x=category, y=predict_fullness_mixed_ED, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE)+
  geom_signif(comparisons = list(c("HighED","LowED")), y_position = 110, map_signif_level = TRUE) +
  geom_boxplot(aes(group = interaction(category, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Energy Density",
       y = "Adjusted anticipated fullness") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(-10, 125) +
  scale_x_discrete(labels = c("HighED" = "Higher",
                              "LowED" = "Lower"))

plot_fullness_ED # need to add significance bar for portion size comparison

```
