---
title: "post-scan rating analyses"
author: "baf44"
date: "1/23/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

Code to plot and analyze liking and fullness ratings

This code uses the following derivative files:

(1) 
(2) 

# Setup

```{r imports, include=FALSE}
library(lme4)
library(lmerTest) # need this to get p-values with anova()
library(plyr)
library(maditr)
library(ggplot2)
library(rstatix)
library(dplyr)
library(psych)
library(emmeans)
library(stringr)
library(ggsignif)
library(performance) # used for check_model()
library(influence.ME) # used for influence()

# Source gen_likefull.R to generate byblock_full_long and byblock_like_long dataframes -- these contain liking and anticipated fullness ratings averaged by food-cue block (long format)
source("R/gen_likefull.R")

```

####  Prepare for parametric analyses #### 

The follow chunk is used to determine what subjects to exclude from parametric analyses

Subjects will be excluded if:
(1) they are missing ratings (fullness, liking) for any block
(2) they do not have enough variability in rating to be included in analyses (must have >1 unique value)

```{r identify subs to exclude}

#### Identify subs with missing ratings for any block ####

# make list subjects with missing fullness data for any block
pm_missing_fullness <- unique(byblock_full_long[is.na(byblock_full_long$avg_fullness),"id"])
pm_missing_fullness # 5 109

# make list subjects with missing behavior for any block
pm_missing_liking <- unique(byblock_like_long[is.na(byblock_like_long$avg_liking),"id"])
pm_missing_liking # 5 109

# count number of subjects with missing data
nrow(pm_missing_fullness) # N = 2
nrow(pm_missing_liking) # N = 2

#### clean data base ####

# remove subjects with missing data
pm_full_temp <- byblock_full_long[ ! byblock_full_long$id %in% pm_missing_fullness, ]
pm_like_temp <- byblock_like_long[ ! byblock_like_long$id %in% pm_missing_liking, ]

# remove runs excluded for motion
censor_sum_subset <- censor_sum[,c("id", "run", "p_censor_interest")]

pm_full_clean <- merge(x=pm_full_temp,y=censor_sum_subset, 
             by=c("id","run"))
pm_full_clean <-pm_full_clean[!(pm_full_clean$p_censor_interest>20),]

pm_like_clean <- merge(x=pm_like_temp,y=censor_sum_subset, 
             by=c("id","run"))
pm_like_clean <-pm_like_clean[!(pm_like_clean$p_censor_interest>20),]

#### Identify subs with  no variability ####

# count number of distinct fullness values by id and ED condition (high, low)
distinct_full_byED <- pm_full_clean %>% group_by(id, category) %>% dplyr::summarize(distinct = n_distinct(avg_fullness))

# count number of distinct fullness values by id and portion condition (large, small)
distinct_full_byPS <- pm_full_clean %>% group_by(id, portion) %>% dplyr::summarize(distinct = n_distinct(avg_fullness))

# count number of distinct liking values by id and ED condition (high, low)
distinct_like_byED <- pm_like_clean %>% filter(cuetype != "office") %>% 
                      group_by(id, category) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# count number of distinct liking values by id and food PS condition (large, small)
distinct_like_byPS <- pm_like_clean %>% filter(cuetype != "office") %>% 
                      group_by(id, portion) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# count number of distinct liking values by id and cue type (large, small)
distinct_like_byCue <- pm_like_clean %>% group_by(id, cuetype) %>% dplyr::summarize(distinct = n_distinct(avg_liking))

# Count subs with no variability in fullness (distinct==1) in at least 1 condition when assessing by ED
novar_full_byED <- distinct_full_byED[(distinct_full_byED$distinct==1),] %>%
  dplyr::summarize(distinct = n_distinct(id))
nrow(novar_full_byED) # N = 0

# Count subs with no variability in fullness (distinct==1) in at least 1 condition when assessing by PS
novar_full_byPS <- distinct_full_byPS[(distinct_full_byPS$distinct==1),] %>%
  dplyr::summarize(distinct = n_distinct(id))
nrow(novar_full_byPS) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by ED
novar_like_byED <- distinct_like_byED[(distinct_like_byED$distinct==1),]
nrow(novar_like_byED) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by PS
novar_like_byPS <- distinct_like_byPS[(distinct_like_byPS$distinct==1),]
nrow(novar_like_byED) # N = 0

# Count subs with no variability in liking (distinct==1) in at least 1 condition when assessing by cue type
novar_like_byCue <- distinct_like_byCue[(distinct_like_byCue$distinct==1),]
nrow(novar_like_byCue) # N = 1
novar_like_byCue$id # 73 ## ID 73 rated 0 for all office supplies


```

```{r visualize variability by condition for each sub}


pm_like_clean$id <- as.factor(pm_like_clean$id)
pm_full_clean$id <- as.factor(pm_full_clean$id)

# Boxplots of liking for HighED foods, by sub
ggplot(pm_like_clean[pm_like_clean$category == "HighED",], aes(x = id, y = avg_liking, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of Liking for HighED Category",
       x = "Person",
       y = "Liking")

# Boxplots of liking for LowED foods, by sub
ggplot(pm_like_clean[pm_like_clean$category == "LowED",], aes(x = id, y = avg_liking, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of Liking for LowED Category",
       x = "Person",
       y = "Liking")

# Boxplots of fullness for HighED foods, by sub
ggplot(pm_full_clean[pm_full_clean$category == "HighED",], aes(x = id, y = avg_fullness, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of fullness for HighED Category",
       x = "Person",
       y = "Fullness")

# Boxplots of fullness for LowED foods, by sub
ggplot(pm_full_clean[pm_full_clean$category == "LowED",], aes(x = id, y = avg_fullness, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of fullness for LowED Category",
       x = "Person",
       y = "Fullness")

# Boxplots of fullness for Large foods, by sub
ggplot(pm_full_clean[pm_full_clean$portion == "Large",], aes(x = id, y = avg_fullness, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of fullness for Large Category",
       x = "Person",
       y = "Fullness")

# Boxplots of fullness for Small foods, by sub
ggplot(pm_full_clean[pm_full_clean$portion == "Small",], aes(x = id, y = avg_fullness, color = id)) +
  geom_point() +
  geom_boxplot() +
  labs(title = "Distribution of fullness for Small Category",
       x = "Person",
       y = "Fullness")
```

```{r count subs included in parametric analyses analyses}

#### count subs included in parametric analyses analyses ####
n_distinct(distinct_full_byED$id)
n_distinct(distinct_full_byPS$id)
n_distinct(distinct_like_byED$id)
n_distinct(distinct_like_byPS$id)
n_distinct(distinct_like_byCue[!(distinct_like_byCue$id==73),]$id) # remove  73 -- no variation in rating for office supplies

```

#### Behavioral analyses ####
The following code analyses liking and fullness by cue type/ED and amount and generates corresponding plots.
Ratings are assessed for all subjects included in non-parametric analyses (n=61).

``` {clean datasets}

# create food-only liking dataframe by removing office conditions
byblock_like_long_food<-byblock_like_long[!(byblock_like_long$cuetype=="office"),]

# remove NAs from liking and fullness data -- not needed to run analyses, but helpful for predicting values to plot results
byblock_like_clean<-byblock_like_long[!is.na(byblock_like_long$avg_liking),]
byblock_like_food_clean <- byblock_like_long_food[!is.na(byblock_like_long_food$avg_liking),]
byblock_full_clean<-byblock_full_long[!is.na(byblock_full_long$avg_fullness),]

# make run variables integers
byblock_like_clean$run <- as.integer(byblock_like_clean$run)
byblock_like_food_clean$run <- as.integer(byblock_like_food_clean$run)
byblock_full_clean$run <- as.integer(byblock_full_clean$run)

# make id variables factor
byblock_like_clean$id <- as.factor(byblock_like_clean$id)
byblock_like_food_clean$id <- as.factor(byblock_like_food_clean$id)
byblock_full_clean$id <- as.factor(byblock_full_clean$id)

```

``` {r assess distributions}

# histograms and density plots of avg_liking by condition
ggplot(byblock_like_clean, aes(x = avg_liking)) + facet_grid(.~cond) + 
  geom_histogram(aes(y = after_stat(density)),
                 colour = 1, fill = "white") +
  geom_density(lwd = 1, colour = 4,
               fill = 4, alpha = 0.25)

# liking distributions are not normal -- skewed (esp for High ED foods) and bounded 

# histograms and density plots of avg_fullness by condition
ggplot(byblock_full_clean, aes(x = avg_fullness)) + facet_grid(.~cond) + 
  geom_histogram(aes(y = after_stat(density)),
                 colour = 1, fill = "white") +
  geom_density(lwd = 1, colour = 4,
               fill = 4, alpha = 0.25)

# fullness distributions are not normal -- bounded 

```

``` {r liking ~ cuetype*portion with lmer}

#### run lmer ####

# liking ~ portion*cue type (food, office)
lmer_liking_cuetype = lmer(avg_liking ~ cuetype*portion + run + (1 | id), data = byblock_like_clean)
anova(lmer_liking_cuetype)


#### test assumptions ####

# Homogeneity of Variance - lmer_liking_cuetype
byblock_like_clean$res.lmer_liking_cuetype<- residuals(lmer_liking_cuetype) # add residuals
byblock_like_clean$Abs.res.lmer_liking_cuetype <-abs(byblock_like_clean$res.lmer_liking_cuetype) #creates a new column with the absolute value of the residuals
byblock_like_clean$Abs2.res.liking_mixed_cuetype <- byblock_like_clean$res.lmer_liking_cuetype^2 #squares the absolute values of the residuals to provide the more robust estimate
Levene.Model_liking_cuetype <- lm(Abs2.res.liking_mixed_cuetype ~ id, data=byblock_like_clean) #ANOVA of the squared residuals
anova(Levene.Model_liking_cuetype) # Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met


leveneTest(residuals(lmer_liking_cuetype) ~ byblock_like_clean$id) # significant (p<.05): violates assumption of equal variances (homoscedasticity) by id
boxplot(residuals(lmer_liking_cuetype) ~ byblock_like_clean$id) # visualize residuals by id

leveneTest(residuals(lmer_liking_cuetype) ~ byblock_like_clean$cuetype) # does not violate assumption
boxplot(residuals(lmer_liking_cuetype) ~ byblock_like_clean$cuetype)

leveneTest(residuals(lmer_liking_cuetype) ~ byblock_like_clean$portion) # does not violate assumption
boxplot(residuals(lmer_liking_cuetype) ~ byblock_like_clean$portion)

# assess random effects (i.e., estimated intercepts for each id) 
# The estimated intercepts represent the expected value of the dependent variable when all predictors are at their reference levels. If your model predicts values outside the permissible range of the dependent variable, it suggests that the model might not be well-specified or might not fit the data appropriately.
ranef(lmer_liking_cuetype)

# fitted vs. residual plots 
plot(liking_mixed_cuetype)
plot(liking_mixed_ED)
# see threads on residual plot that looks similar to this:
# https://stats.stackexchange.com/questions/120751/not-sure-about-the-interpretation-of-this-residual-plot
# https://stats.stackexchange.com/questions/524078/assumptions-of-linearity-and-homoskedasticity-when-the-dv-is-a-likert-scale-ho 
# the tilt in the plot is due to the boundedness of the DV (liking is assessed on scale from 0-100)

# qq plots
qqnorm(resid(liking_mixed_cuetype))
qqline(resid(liking_mixed_cuetype))



qqmath(ranef(liking_mixed_cuetype, condVar = TRUE), strip = FALSE)$id



# Homogeneity: Need to Check by plotting residuals vs predicted values.
# Note that "residuals" above refer to both the unit-level residuals (often called "errors") and the random effects. For the random effects, this can be problematic where only a small number of groups/clusters exist in the sample. In the simulated example given in the OP there are 7 clusters. There are lots of rules of thumb to inform a sufficient number of clusters, and 7 is generally thought to be difficult to draw any conclusions.

# Normality of error term: need to check by histogram, QQplot of residuals, even Kolmogorov-Smirnov test.


ggplot(data = byblock_like_clean, aes(predict_liking_mixed_cuetype, res_liking_mixed_cuetype)) +
  geom_point() +
  facet_grid( ~ cond ) + geom_smooth(method='lm')

# https://rdrr.io/cran/nlme/man/qqnorm.lme.html

qqnorm(resid(liking_mixed_cuetype))
qqline(resid(liking_mixed_cuetype))


#### get estimated marginal means and SEs ####
emmeans(lmer_liking_cuetype, specs = pairwise ~cuetype|portion, type = "response")
emmeans(lmer_liking_cuetype, specs = pairwise ~cuetype, type = "response")

```


``` {r liking ~ ED*portion with lmer}

#### ANALYSES ####

# liking ~ portion*ED (category = highED, lowED)
lmer_liking_ED = lmer(avg_liking ~ category*portion + run + (1 | id), data = byblock_like_food_clean)

anova(lmer_liking_ED)

# get estimated marginal means and SEs
emmeans(lmer_liking_ED, specs = pairwise ~category|portion, type = "response")
emmeans(lmer_liking_ED, specs = pairwise ~category, type = "response")


#### Test assumptions ####

# Homogeneity of Variance - lmer_liking_ED
byblock_like_food_clean$res.lmer_liking_ED<- residuals(lmer_liking_ED) # add residuals 
byblock_like_food_clean$Abs.res.lmer_liking_ED <-abs(byblock_like_food_clean$res.lmer_liking_ED) #creates a new column with the absolute value of the residuals
byblock_like_food_clean$Abs2.res.lmer_liking_ED <- byblock_like_food_clean$res.lmer_liking_ED^2 #squares the absolute values of the residuals to provide the more robust estimate
Levene.Model_liking_ED <- lm(Abs2.res.lmer_liking_ED ~ id, data=byblock_like_food_clean) #ANOVA of the squared residuals
anova(Levene.Model_liking_ED) # Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met

leveneTest(residuals(lmer_liking_ED) ~ byblock_like_food_clean$id) # significant
boxplot(residuals(lmer_liking_ED) ~ byblock_like_food_clean$id) # visualize residuals by id

leveneTest(residuals(lmer_liking_ED) ~ byblock_like_food_clean$category) # does not violate assumption
boxplot(residuals(lmer_liking_ED) ~ byblock_like_food_clean$category)

leveneTest(residuals(lmer_liking_ED) ~ byblock_like_food_clean$portion) # does not violate assumption
boxplot(residuals(lmer_liking_ED) ~ byblock_like_food_clean$portion)

# fitted vs. residual plots 
plot(lmer_liking_ED)

# fitted vs. residual plots - color by ID
plot(lmer_liking_ED, resid(., scaled=TRUE) ~ fitted(.), abline = 0,pch=16,col=byblock_like_food_clean$id,xlab="Fitted values",ylab="Standardised residuals")

# fitted vs. residual plots - facet by id
plot(lmer_liking_ED, resid(., scaled=TRUE) ~ fitted(.)| id, abline = 0,pch=16,xlab="Fitted values",ylab="Standardised residuals")

#compare the difference in residuals between random effect levels using default boxplots
plot(lmer_liking_ED, as.factor(id) ~ resid(., scaled=TRUE),abline=0,pch=16,xlab="Standardised residuals",ylab="IDs")

# see threads on residual plot that looks similar to this:
# https://stats.stackexchange.com/questions/120751/not-sure-about-the-interpretation-of-this-residual-plot
# https://stats.stackexchange.com/questions/524078/assumptions-of-linearity-and-homoskedasticity-when-the-dv-is-a-likert-scale-ho 
# the tilt in the plot is due to the boundedness of the DV (liking is assessed on scale from 0-100)

library(performance)
check_model(lmer_liking_ED)

# qq plot with qq line
lattice::qqmath(lmer_liking_ED)

# leverage (hatvalues) against standardised residuals plot
plot(lmer_liking_ED, rstudent(.) ~ hatvalues(.))

library(influence.ME)
infl <- influence(lmer_liking_ED, group = "id")
cooks.distance(infl)
plot(infl, which = "cook")



#Calculate Cook's Distance
cd.lmer_liking_ED<-cooks.distance(lmer_liking_ED)
#N.B. If Cook's distance is greater than 1 this highlights problematic datapoints

#Plot leverage and Cook's distance together
par(mfrow=c(1,1))
plot(lev.lmer_liking_ED,pch=16,col="red",ylim=c(0,1.2),las=1,ylab="Leverage/Cook's distance value")
points(cd.lmer_liking_ED,pch=17,col="blue")
points(x=150,y=1.1,pch=16,col="red")
points(x=150,y=0.9,pch=17,col="blue")
text(x=155,y=1.1,"Leverage",adj=c(0,0.5))
text(x=155,y=0.9,"Cook's distance",adj=c(0,0.5))

qqmath(ranef(liking_mixed_cuetype, condVar = TRUE), strip = FALSE)$id
lattice::qqmath(lmer_liking_ED)



# Homogeneity: Need to Check by plotting residuals vs predicted values.
# Note that "residuals" above refer to both the unit-level residuals (often called "errors") and the random effects. For the random effects, this can be problematic where only a small number of groups/clusters exist in the sample. In the simulated example given in the OP there are 7 clusters. There are lots of rules of thumb to inform a sufficient number of clusters, and 7 is generally thought to be difficult to draw any conclusions.

# Normality of error term: need to check by histogram, QQplot of residuals, even Kolmogorov-Smirnov test.


ggplot(data = byblock_like_clean, aes(predict_liking_mixed_cuetype, res_liking_mixed_cuetype)) +
  geom_point() +
  facet_grid( ~ cond ) + geom_smooth(method='lm')


# https://rdrr.io/cran/nlme/man/qqnorm.lme.html

qqnorm(resid(liking_mixed_cuetype))
qqline(resid(liking_mixed_cuetype))
qqnorm(resid(liking_mixed_ED))
qqline(resid(liking_mixed_ED))



```


``` {r fullness analyses with lmer}
# fullness ~ portion size (large, small) x ED (category = highED, lowED)
lmer_fullness_ED = lmer(avg_fullness ~ category*portion + run + (1 | id), data = byblock_full_clean)
anova(lmer_fullness_ED)

check_model(lmer_fullness_ED)


# get estimated marginal means and SEs
emmeans(lmer_fullness_ED, specs = pairwise ~portion, type = "response")
emmeans(lmer_fullness_ED, specs = pairwise ~category, type = "response")
emmeans(lmer_fullness_ED, specs = pairwise ~portion|category, type = "response")
emmeans(lmer_fullness_ED, specs = pairwise ~category|portion, type = "response")


```

Figure 1:
``` {r adjusted liking and fullness violin plots }

# get adjusted response after adjusting for covariates in model 
byblock_like_clean$predict_lmer_liking_cuetype <- predict(lmer_liking_cuetype, type="response")
byblock_like_food_clean$predict_lmer_liking_ED <- predict(lmer_liking_ED, type="response")
byblock_full_clean$predict_lmer_fullness_ED <- predict(lmer_fullness_ED, type="response")


#### VIOLIN PLOTS with ggplot####

# liking ~ amount x cue type -- plot adjusted 
plot_liking_cuetype <- ggplot(byblock_like_clean, aes(x=cuetype, y=predict_lmer_liking_cuetype, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE) +
  geom_signif(comparisons = list(c("food","office")), y_position = 115, map_signif_level = TRUE) +
  geom_boxplot(aes(group = interaction(cuetype, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Cue Type",
       y = "Adjusted liking") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(-10, 125) + 
  scale_x_discrete(labels = c("food" = "Food",
                              "office" = "Office Supplies"))


plot_liking_cuetype

# liking ~ amount x ED (category)
plot_liking_ED <- ggplot(byblock_like_food_clean, aes(x=category, y=predict_lmer_liking_ED, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE)+
  geom_signif(comparisons = list(c("HighED","LowED")), y_position = 115,
              map_signif_level = TRUE) +
  geom_boxplot(aes(group = interaction(category, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Energy Density",
       y = "Adjusted liking") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(-10, 125) +
  scale_x_discrete(labels = c("HighED" = "Higher",
                              "LowED" = "Lower"))

plot_liking_ED

# fullness ~ amount x ED
plot_fullness_ED <- ggplot(byblock_full_clean, aes(x=category, y=predict_lmer_fullness_ED, fill = portion)) +
  theme_bw() +
  geom_violin(trim=FALSE)+
  geom_boxplot(aes(group = interaction(category, portion)), fill = 'white', position = position_dodge(width = 0.9),  width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values = c("lightgrey", "grey35")) +
  labs(x="Energy Density",
       y = "Adjusted anticipated fullness") +
  theme(legend.title = element_blank()) +
  theme(axis.text=element_text(size=12, color = "black"), axis.title=element_text(size=14,face="bold")) + 
  ylim(-10, 125) +
  scale_x_discrete(labels = c("HighED" = "Higher",
                              "LowED" = "Lower")) +
  geom_signif(comparisons = list(c("HighED", "LowED")), y_position = 115, map_signif_level = TRUE)

plot_fullness_ED +
  geom_signif(
    y_position = c(105, 105), xmin = c(0.8, 1.8), xmax = c(1.2, 2.2),
    annotation = c("***", "***"), tip_length = .03
  )


library(ggpubr)

plot_fullness_ED +
  stat_compare_means(comparisons = list(c("HighED", "LowED"), c("Large", "Small")),
                     label = "p.signif",
                     method = "t.test",
                     textsize = 5,
                     test.shortname = c("category", "portion"),
                     vjust = 0.5,
                     position = position_dodge(width = 0.9))

plot_fullness_ED

```

``` {r liking and fullness plots - alternative }

#### with sjplot #### 
#install.packages("sjPlot")
library(sjPlot)

### plot predicted values (marginal effects) with sjPlot
# type = "int" plots marginal effects of interaction terms in model

plot_model(lmer_liking_cuetype, type = "int", ci.lvl = 0.95) + ylim(0, 100)
plot_model(lmer_liking_ED, type = "int", ci.lvl = 0.95) + ylim(0, 100)
plot_model(lmer_fullness_ED, type = "int", ci.lvl = 0.95) + ylim(0, 100)

### plot estimates with sjPlot
plot_model(lmer_liking_cuetype, show.values = TRUE)
plot_model(lmer_liking_ED, show.values = TRUE)
plot_model(lmer_fullness_ED, show.values = TRUE)

### plot predicted value manually

quartiles_by_group <- byblock_like_clean %>%
  group_by(cuetype, portion) %>%
  summarize(
    Q1 = quantile(predict_lmer_liking_cuetype, 0.25),
    Q3 = quantile(predict_lmer_liking_cuetype, 0.75)
  )
print(quartiles_by_group)

# boxplot
ggplot(byblock_like_clean, aes(x = cuetype, y = predict_lmer_liking_cuetype, fill = portion)) +  
geom_boxplot(outlier.shape = NA)+ 
geom_point(position = position_jitterdodge(), alpha=0.3) 


#### dotplot with ggplot####
# box + dot plot -- average liking (not predicted)
p<-ggplot(byblock_like_clean, aes(x=cuetype, y=avg_liking, fill = portion)) +
  geom_boxplot(position=position_dodge(0.8)) +
  geom_dotplot(binaxis='y', stackdir='center', 
               position=position_dodge(0.8), dotsize=.2)

p

# box + dot plot -- adjusted (predicted) liking
p_adj<-ggplot(byblock_like_clean, aes(x=cuetype, y=predict_lmer_liking_cuetype, fill = portion)) +
  geom_boxplot(position=position_dodge(0.8)) +
  geom_dotplot(binaxis='y', stackdir='center', 
               position=position_dodge(0.8), dotsize=.2) +
    ylim(0, 100)

p_adj


```
